SemanticPaint

### 2015-12-09 cv3d_seminar/presentation.tex
finished notes, add Q&A slide with SemanticPaint diagram
add inline notes

\documentclass[mathserif, 10pt]{beamer}
\input{macro}

% \usepackage[font=footnotesize,labelfont=bf]{caption}
% \setbeamerfont{caption}{size=\scriptsize}

@@

\begin{frame}
\titlepage
\end{frame}

@@

\begin{frame}{Outline}
\tableofcontents
\end{frame}

@@

  Herbst et. al. 2014  & reconstruction & online model updates \\
     & segmentation & change detection\\ \hline

 \end{tabular}
}
\end{table}

@@

@@

@@

\begin{columns}
 \begin{column}{0.5\textwidth}
  \begin{figure}
  \center
  \includegraphics[width=\textwidth]{figures/vop}
  \caption{Colours shown in RGB for illustration purposes.}
  \label{fig:vop}
\end{figure}
 \end{column}
 \begin{column}{0.5\textwidth}
    $(\mathbf{p} - \mathbf{p}_i) \cdot \mathbf(n)_i = 0$ \\
    $r \times r$, $r = 13px$ with $10\frac{mm}{pixel}$\\
    CIELab\\
    Rotated to dominant gradient direction

 \end{column}

@@

  \vspace{-0.25cm}
  $H(R_n)$ computed from a node's class distribution
\end{frame}

@@

@@

\begin{frame}
\frametitle{CRF - User Interactions}
% \vspace{-1cm}
  Touching:
  \begin{columns}
   \begin{column}{0.25\textwidth}
    \begin{figure}
    \includegraphics[width=\textwidth]{figures/touch}
    \end{figure}
    \end{column}
    \begin{column}{0.75\textwidth}
      \begin{equation}
	\phi_i(l) =
	  \begin{cases}
	    0      & \quad \text{if } l = l_T\\
	    \infty  & \quad \text{otherwise}\\
	  \end{cases}
      \end{equation}
      \center
      $T$ --- touched pixels
   \end{column}

@@

  \center
  $P_E$ from GMM\\
  fg --- inside\\
  bg --- outside
   \end{column}

@@

@@

@@

@@

@@

\begin{frame}
\frametitle{Features}
\vspace{-0.25cm}
 \begin{figure}[!ht]
  \center
  \includegraphics[width=\textwidth]{figures/results_vop}
%   \caption{Average Precision}
%   \label{fig:srf_ap}
  \end{figure}
\end{frame}

@@

@@

 \begin{column}{0.5\textwidth}
  Data:\\
  300 objects\\
  51 classes\\
  full revolution\\
  3 points of view \\
  \vspace{0.5cm}
  SRF - Streaming Random Forest\\
  ORF - Online Random Forest\\
  HT - Hoeffding Tree \\
 \end{column}
\end{columns}
\end{frame}

@@

@@

\begin{frame}
\frametitle{Future Work}
\begin{itemize}
 \item class priors for different enviornments
 \item priors for class properties (vertical walls)
 \item discriminative geometrical features
 \item outdoor enviornments
 \item better scalability
\end{itemize}

@@

>>>>

\documentclass[mathserif, 10pt]{beamer}
\input{macro}
\usepackage{pdfpcnotes}
\usepackage{multimedia}
% \usepackage[font=footnotesize,labelfont=bf]{caption}
% \setbeamerfont{caption}{size=\scriptsize}

@@

\begin{frame}
\titlepage
\pnote{name}
\pnote{framework for interactive capturing of 3D enviornments}
\end{frame}

@@

\begin{frame}{Outline}
\tableofcontents
\pnote{Let's start by seeing the framework in action}
\end{frame}

@@

  Herbst et. al. 2014  & reconstruction & online model updates \\
     & segmentation & change detection\\ \hline
 \end{tabular}
}
\end{table}

\pnote{research on: RFB, D, point cloud, mesh, volume}
\pnote{most offline, not real time; CNN for class & detetect, CRF and variation for segm}
\pnote{Valentin}
\pnote{depth into volumetric TSDF, triangulated, mesh}
\pnote{rgb on img, geo on mesh}
\pnote{KITTI, NYU; mesh speed and accuracy}
\pnote{}
\pnote{Kim}
\pnote{voxel <- visibility and occupancy, vis constrained}
\pnote{model and reduce noise in depth maps}
\pnote{offline, global inference}
\pnote{}
\pnote{Herbst}
\pnote{detect change after model updates}
\pnote{static unchanged, dynamic changed}
\pnote{online but not real time, 2s per frame}

@@

\pnote{SLAM important in robotics, SemanticPaint relies heavily}
\pnote{major contribution by Newcombe, KinectFusion; 3D reconstruction from a single depth sensor}
\pnote{model-based tracking to match frame against model}
\pnote{global volume in TSDF}
\pnote{}
\pnote{extends KinectFusion -> object classification}
\pnote{match objects from the scene against a database}
\pnote{obj-pose graph, sparse, compact repr}
\pnote{sparse, requires offline database}
\pnote{}
\pnote{3D from single RGB camera}
\pnote{tracking, key and secondary frames, stereo reconsutrction}
\pnote{small scenes, good performance for textured}
\end{frame}

@@

\pnote{depth + rgb = TSDF}
\pnote{user interactions = touched obj into CRF => priors}
\pnote{also into RF => predict labels for other objects}
\pnote{feedback loop: CRF gives labels from SRF, RF is trained on CRF}
\end{frame}

\begin{columns}
 \begin{column}{0.5\textwidth}
  \begin{figure}
  \center
  \includegraphics[width=\textwidth]{figures/vop}
  \caption{Colours shown in RGB for illustration purposes.}
  \label{fig:vop}
\end{figure}
 \end{column}
 \begin{column}{0.5\textwidth}
    $(\mathbf{p} - \mathbf{p}_i) \cdot \mathbf(n)_i = 0$ \\
    $r \times r$, $r = 13px$ with $10\frac{mm}{pixel}$\\
    CIELab\\
    Rotated to dominant gradient direction
 \end{column}
\end{columns}

@@

@@

  \vspace{-0.25cm}
  $H(R_n)$ computed from a node's class distribution

  \pnote{SRF inherently online; some terminology}
  \pnote{the behind the reservoir: samples over huge time window -> unbiased sample of all data}
  \pnote{objective: Information Gain from normalized class distribution at each node}
\end{frame}

@@

\pnote{create node + distribution of split functions}
\pnote{split node -> sweep through R for every split function and compute class distributions}
\pnote{no explicit R computations are needed, just the splits}
\pnote{pass the statistics to child nodes}
\end{frame}

@@

\pnote{CRFS subclass of PGMs; classification of sequences; global contex}
\pnote{in CV: segmentation; here: smoot out segm and user inter}
\pnote{}
\pnote{psi - likelihood and prior}
\pnote{distr -> NLL -> energy -> minimize}
\pnote{phi -> cost of label, smoothnes}
\pnote{eps -> neigbourhood, 6cm}
\end{frame}

\begin{frame}
\frametitle{CRF - User Interactions}

  Touching:
  \begin{columns}
   \begin{column}{0.25\textwidth}
    \begin{figure}
    \includegraphics[width=\textwidth]{figures/touch}
    \end{figure}
    \end{column}
    \begin{column}{0.75\textwidth}
      \begin{equation}
	\phi_i(l) =
	  \begin{cases}
	    0      & \quad \text{if } l = l_T\\
	    \infty  & \quad \text{otherwise}\\
	  \end{cases}
      \end{equation}
      \center
      $T$ --- touched pixels
   \end{column}

@@

  \center
  $P_E$ from GMM\\
  fg --- inside\\
  bg --- outside
   \end{column}
  \end{columns}

\pnote{Note -> changing energy landscape <- user interactions}
\pnote{touch and say -> set potentials; 0 if correct or inf otherwise}
\pnote{}
\pnote{circle more complication -> convex hull of selection as fg, others bg}
\pnote{fit GMM and infer in a boundix box around selection}
\pnote{to update potentials}
\end{frame}

@@

\pnote{Next come forest predictions -> update pot of otherwise unaffected voxels -> NLL of current class}
\pnote{smothness -> priors based on differences}
\end{frame}

@@

\pnote{Then comes mean-field inference}
\pnote{approximate original P(x) under KL with Q(x)}
\pnote{iterative algo to refine}
\pnote{gradual change of energy landscape}
\pnote{single update in each frame}
\pnote{to speed up RF's impact -> initialization}
\end{frame}

@@

\pnote{Let's look at some segmentation results}
\pnote{We have... for 2 different scenes}
\pnote{inference improves results quite a lot}
\pnote{we can relabel and correct mistakes}
\end{frame}

@@

\pnote{if we look at percentage}
\pnote{iteraction very well}
\pnote{RF ok}
\pnote{mean-field smoothing improves}
\end{frame}

\begin{frame}
\frametitle{Features}
\vspace{-0.25cm}
 \begin{figure}[!ht]
  \center
  \includegraphics[width=\textwidth]{figures/results_vop}
%   \caption{Average Precision}
%   \label{fig:srf_ap}
  \end{figure}

\pnote{Next, let's look at features}
\pnote{compared indirectly by comparing how RF behaves while using different features}
\pnote{discriminative power}
\pnote{here: 3 best results; VOP most consistent}

@@

@@

\pnote{Again, if we look at percentage, VOP the best}
\pnote{Kitchen is worse -> harsh illumination}
\pnote{makes RGB feature inconclusive}
\end{frame}

@@

 \begin{column}{0.5\textwidth}
  Data:\\
  300 objects\\
  51 classes\\
  full revolution\\
  3 points of view \\
  \vspace{0.5cm}
  SRF - Streaming Random Forest\\
  ORF - Online Random Forest\\
  HT - Hoeffding Tree \\
 \end{column}
\end{columns}

\pnote{SRF against two other tree-based online classifiers ORF and HT}
\pnote{simulate online setting: add new classes and PoVs sequentially}
\pnote{SRF outperforms comfortably, more effiiicient}
\pnote{Sad fact: accurayc drops with classes}
\pnote{handling coplicated scenes tricky}
\end{frame}

@@

\pnote{To sum up: delivers pipeline that lets capture personalized 3D envs as you need}
\pnote{fully interactive, req no pretrain and works online}
\pnote{possible apps: robot navi, sighted people, datasets for large-scale CV}
\end{frame}

@@

\pnote{Unf, some failures}
\pnote{Bleeding, or misclassif at object edges <- errors of depth and colour sensor alignm}
\pnote{big illumination and viewpoint changes -> errors}
\end{frame}

\begin{frame}
\frametitle{Future Work}
\begin{itemize}
  \item discriminative geometrical features
  \item priors for class properties (vertical walls)
 \item class priors for different enviornments
 \item outdoor enviornments
 \item better scalability
\end{itemize}

\pnote{Some future work to be done}
\pnote{Geo features -> prevent bleeding}
\pnote{class priors (vertical walls) and for diff envs -> better accuracy}
\pnote{outdoor envs -> passive sensors}
\pnote{bigger scenes and more classes -> scalable algos}
\end{frame}

@@

\begin{frame}
\frametitle{Q\&A?}
\begin{figure}
 \includegraphics[width=0.8\textwidth]{figures/SemanticPaint}
\end{figure}
